\chapter{Introduction}

But if you teach your computer to fish..


\section{Motivation}
There are many great resources that exist.

I wanted to create the guide I wish I found.

\textcolor{blue}{ML -- study of how programs learn from data. predictive analytics or statistical learning.}



\section{What \& Why ML}
\textcolor{blue}{Arthur Samuel -- ``ML is the study that gives computers the ability to learn without being explicitly programed.''}

\textcolor{blue}{Tom Mitchel -- ``A program can be said to learn from experience `E' with respect to some class of tasks `T' and performance measure `P', if its performance at tasks in `T', as measured by `P', improves with experience `E'.''}

\textcolor{blue}{ML is everywhere.... everyday --- personalized music, show,book,product recommendations, automatic image tagging to specific tasks, detecting fraudulent credit card activity -- analyzing medical images (benign, or malignant). }

\textcolor{green}{TODO: venn diagram, AI (knowledge bases -- logical inference rules (cyc))-> Machine Learning  (SVM, Logistic Regression, naive bayes) -> Representation Learning (...), Deep Learning (MLP, Deep CNN, RNN)}

% p.4 of DL
\textcolor{red}{Representation learning: learn the representation from from input to output, not just the mapping.}

\subsection{Deep Learning}


\textcolor{blue}{Model depth --- depends on the definition of what is considered a computational step --- what level of detail is being considered. This may be either the length of the longest path through the computational graph, where each multiplication, addition, etc. are considered, or this may be described by how the concepts are related to one another, where a group of opperations may be grouped together for a single count (such as in a dense or convolutional layer). In general, we will not be overly concerned with depth or how it is described. It is only important to be aware that some individuals may have different definitions for ``deep'' than others.}

\subsubsection{Why Now?}

\textcolor{blue}{Why is deep learning suddenly so popular?}

\textcolor{blue}{Deep learning is nothing ``new''. It has been rebranded, i.e. gone by many different names \textcolor{green}{cybernetics (1940s-1950s), connectionism (1980s-1990s), deep learning ($\approx 2006$) more prev+new examples} and its popularity has increased and decreased over time.}

\textcolor{green}{``Deep Learning = new electricity'' - Ng}

\textcolor{blue}{A few reasons that may be contributed to the recent surge in popularity may be the following:}

\begin{itemize}
	
	\item \textit{More Data}: \textcolor{blue}{information about the increase in the collection of data}.
	
	\item \textit{Computational Power/Price}: \textcolor{blue}{GPUs, TPUs, examples of price -- both clock freq, number cores, memory, bandwidth}.
	
	\item \textit{Performance Benchmarks}: \textcolor{blue}{Examples like imagenet}.
	
\end{itemize}


\section{Notes}

\subsection{Target Audience}
\textcolor{blue}{target audience: XXXXXXX}

\subsection{How to Read this Book}
\textcolor{blue}{sequential}

\textcolor{blue}{section by section (jk)}

\textcolor{green}{TODO: figure of the structure of the book. I really like figure 1.6 in DL}


